Methods

### 2019-01-21 Methods.Rmd
updated

save(SACTN_daily_temps_indexsplit, file = "SACTN_daily_temps_indexsplit.RData")
```

@@

# SACTN_daily_temps_indexsplit <- SACTN_monthly(df = SACTN_daily_temps_indexsplit)
# save(SACTN_daily_temps_indexsplit, file = "SACTN_daily_temps_indexsplit.RData")
```

@@

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/SACTN_daily_temps_indexsplit.RData")
SACTN_3yr <- SACTN_daily_temps_indexsplit %>% 
  filter(year(date) %in% seq(1998, 1999, 2000))
```

@@

match_func <- function(df){
  match <- SACTN_daily_temps_indexsplit  %>% 
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

>>>>

# save(SACTN_daily_temps_indexsplit, file = "Data/SACTN_daily_temps_indexsplit.RData")
```

@@

SACTN_split <- SACTN_monthly(df = SACTN_daily_temps_indexsplit)
save(SACTN_split, file = "SACTN_split.RData")
```

@@

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/SACTN_split.RData")

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(1998, 1999, 2000))
```

@@

match_func <- function(df){
  match <- SACTN_split  %>% 
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}
